Summary Tables

### 2019-12-18 summary_tables.Rmd
Add capetown and vizag

```{r load_objects = "asis"}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
cities <- c('accra','sao_paulo','delhi','bangalore', 'santiago', 'belo_horizonte', 'buenos_aires', 'mexico_city','bogota')

@@

>>>>

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
cities <- c('accra','sao_paulo','delhi','bangalore', 'santiago', 'belo_horizonte', 'buenos_aires', 'mexico_city','bogota', 'cape_town', 'vizag')

@@

|cape_town|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 70.8|23.9|2.3 |
| bicycle | 0.0|0.5|0.4 |
| car | 7.5|47.2|54.6 |
| motorcycle | 0.0|0.3|0.7 |
| bus | 1.6|28.1|42.1 |

|vizag|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 81.4|19.6|0.1 |
| bicycle | 3.9|7.6|1.9 |
| car | 0.6|2.5|2.2 |
| motorcycle | 9.6|25.4|22.9 |
| bus | 0.1|21.7|56.1 |
